---
output:
  github_document:
    fig_width: 10
    fig_height: 8
    df_print: kable
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse=TRUE,
  warning=FALSE,
  message=FALSE,
  comment="#>",
  fig.path="man/figures/README-",
  out.width="100%"
)
options(knitr.table.format='markdown')
```

# pajam

<!-- badges: start -->
<!-- badges: end -->

The goal of pajam is to provide data and visualizations from Protein Atlas,
whose data is graciously provided by https://proteinatlas.org.

## Installation

You can install `pajam` from [GitHub](https://github.com/) with:

``` r
# install.packages("remotes")
remotes::install_github("jmw86069/pajam")
```

## Example

Display protein tissue expression for a set of genes, displaying
only `"Tissue"` sample types:

```{r pajam_example}
library(pajam)

test_genes <- c("DKK1","DKK4","CXCL12","IL6R","MET",
   "HK2","FTL","FTH1","STAT1","STAT3","CDKN1B");
rowGroupMeans <- jamba::rowGroupMeans;
proteinatlas_heatmap(genes=test_genes,
   type="Tissue",
   centered=TRUE);
```

This package includes a few useful genesets that may provide
useful context into the genes. The following example shows
`"Blood"` sample types, and some added annotations.

```{r pajam_genesets}
# use proteinatlas_genesets_fdb11
use_im <- c("secreted_proteins",
   "membrane_proteins",
   "NOT_membrane_secreted",
   "TFs");
proteinatlas_im <- list2im_opt(proteinatlas_genesets_fdb11[use_im]);
proteinatlas_heatmap(genes=test_genes,
   type="Blood",
   centered=TRUE,
   gene_im=proteinatlas_im);
```

You can filter samples to require a certain minimum expression:

```{r pajam_filter}
proteinatlas_heatmap(genes=test_genes,
   type=c("Tissue","Blood"),
   centered=TRUE,
   column_filter=16,
   gene_im=proteinatlas_im);
```

It may be useful in finding cell line expression for a subset of
genes:

```{r pajam_cells}
proteinatlas_heatmap(genes=c("ACE2", "TMPRSS2", "FOXJ1", "HOPX", "SFTPC"),
   type=c("Cell"),
   centered=TRUE,
   column_filter=4,
   cluster_columns=TRUE,
   gene_im=proteinatlas_im);
```
